---
title: "ETL-process for retrieval of ECDC Corona-data"
author: "G. Versteeg"
date: "27/09/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is an ETL Markdown document, to retrieve corona data from ECDC. 

The European Centre for Disease Prevention and Control is located at:
source: https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide

We will schedule this retrieval weekly and pin the resulting dataset ont a RS-Connect board.

## Housekeeping

```{r housekeeping}
## housekeeping
library(utils)
library(httr)
library(tidyverse)



```


## Getting and cleaning the data

Download the dataset from ECDC to a local temporary file and copy into DF data

```{r}
## get dataset
GET("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv", 
    authenticate(":", ":", type="ntlm"), 
    write_disk(tf <- tempfile(fileext = ".csv")))
data <- read.csv(tf)

## clean dataset
  mutate(Rpt_date = as.Date(as.character(dateRep), "%d/%m/%Y")) %>% 
  mutate(Cont_rate = cases / popData2019 * 100)

```

```{r}

df_cln <- data
df_cln

```

## Plotting the resulting dataset 

```{r}

  ## plotting the data
  df_cln %>% 
    filter(countriesAndTerritories == "Netherlands") %>% 
    ggplot(aes(Rpt_date, Cont_rate)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format())

...




```

```{r}
df_cln %>% 
    filter(countriesAndTerritories == "Netherlands","Germany")) 
```


```

