---
title: "ETL-process for retrieval of ECDC Corona-data"
author: "G. Versteeg"
date: "27/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is an ETL Markdown document, to retrieve corona data from ECDC. 

The European Centre for Disease Prevention and Control is located at:
source: https://www.ecdc.europa.eu/en/publications-data/download-todays-data-geographic-distribution-covid-19-cases-worldwide

We will schedule this retrieval weekly and pin the resulting dataset ont a RS-Connect board.

## Housekeeping

```{r housekeeping}
## housekeeping
library(utils)
library(httr)
library(tidyverse)
library(pins)

# Register the RS-Connect board
# Pins will use CONNECT_API_KEY and CONNECT_SERVER by default,
# but we are being explicit here anyway.
pins::board_register_rsconnect(
  key = Sys.getenv("CONNECT_API_KEY"), 
  server = Sys.getenv("CONNECT_SERVER")
)

```


## Getting and cleaning the data

Download the dataset from ECDC to a local temporary file and copy into DF data

```{r}
## get dataset
GET("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv", 
    authenticate(":", ":", type="ntlm"), 
    write_disk(tf <- tempfile(fileext = ".csv")))
data <- read.csv(tf)

## clean dataset
df_cln <- data %>%
  mutate(Rpt_date = as.Date(as.character(dateRep), "%d/%m/%Y")) %>% 
  mutate(Cont_rate = cases / popData2019 * 100)

```

## Pinning the resulting dataset to a board

```{r}
pins::pin(df_cln, name = "pin_corona", 
          description = "Weekly corona data from ECDC", board = "rsconnect")
```

